%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ephraim Teodoro } \\ \vspace{1pt}
    \small808-897-0839   $|$ \href{mailto:x@x.com}{\underline{ephraim29@go.byuh.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/teodoro-e/}} $|$
    \href{https://github.com/...}{\underline{github.com/EPHRAIMTEODORO}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Enterprise Information Systems Developer}{Feb. 2025 -- Present}
  {Brigham Young University-Hawaii}{Laie, HI}
  \resumeItemListStart
    \resumeItem{Utilized React.js to create a front-end formatting tool for department use, supporting JSON, XML, SQL, HTML, CSS, and URL-encoded formats reducing the time of making server logs into readable format by 50 percent}
    \resumeItem{Developed a C\# ASP.NET club management system with TeamDynamix integration and a MySQL-backed API layer, streamlining event requests to save 3 days of processing and reducing API calls by 67\%.  }
    \resumeItem{Utilized ASP.NET  and Mendix Application development Platform to assist in software and network development task ensuring seamless functionality.}
    \resumeItem{Implemented a backend feature that detects incorrect credentials during ELAT applicant renewal, automatically generating and sending alert emails to designated recipients.}
    \resumeItem{Updated the frontend of the university's student onboarding website to align with new branding guidelines.}
    \resumeItem{Generated Docker images for development environment testing and used Docker for containerization.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
\section{Relevant Activities}
    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{Tourism-Visualization} $|$ \emph{Javascript, CSS, D3js, REST API, Postgresql}}{Feb. 2026}
          \resumeItemListStart
            \resumeItem{Built an interactive data visualization tool using D3.js v7 to compare standard and bubble scatter plots for tourism data analysis}
            \resumeItem{Integrated a Netlify serverless function with a Neon Postgres backend to collect and store research participant survey responses}
            \resumeItem{Processed UN tourism CSV datasets, normalizing arrival and expenditure figures across countries and years}
            \resumeItem{Designed a responsive frontend using Flexbox and SVG viewBox scaling}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Learn-Kana Web App} $|$ \emph{Next.js 14, TypeScript, Tailwind CSS}}{2025}
          \resumeItemListStart
            \resumeItem{Engineered an interactive Japanese character learning web application with flashcards, quizzes, and progress tracking using Next.js 14, TypeScript, and Tailwind CSS.}
            \resumeItem{Implemented client-side state persistence via the browser localStorage API to capture learning analytics, including accuracy rates and character mastery, without authentication.}
            \resumeItem{Designed and optimized a responsive, mobile-first interface supporting multiple learning modes (Hiragana, Katakana, mixed) with real-time feedback.}
            \resumeItem{Validated application effectiveness through production use, achieving complete Hiragana acquisition within two weeks.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Simple University Demo-API} $|$ \emph{ASP.NET, C\#, MySQL, REST API}}{Feb. 2025}
          \resumeItemListStart
            \resumeItem{Developed a University Management REST API using ASP.NET and MySQL, delivering full CRUD functionality for Teachers, Students, Courses, and Enrollments.}
            \resumeItem{Designed and implemented a normalized relational database schema with optimized SQL queries to ensure data integrity and performance.}
            \resumeItem{Architected RESTful endpoints to support frontend integration and role-based data operations.}
            \resumeItem{Tested and validated API endpoints using Postman while maintaining clean architecture through controllers, services, and models.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML, CSS, MySQL, C-sharp, Javascript, Java} \\
     \textbf{Frameworks}{: ASP.NET,  React} \\
     \textbf{Developer Tools}{: Git, Github, Microsoft VS Code, Postman, IntelliJ IDEA, Android Studio, Microsoft visual Studio, Docker} \\
     \textbf{Skills}{: Fundamentals, Object-Oriented Programming, Database
Management, Systems Engineering, Web Application Development, Discrete Math
}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brigham Young University - Hawaii}{Laie, HI}
      {Bachelor of Science in Computer Science, Minor in Visual Arts}{Jan. 2023 -- Dec. 2026}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}